### 2022-08-22 doc/TrashData.tex
minor edits to trashsims table

\caption{\label{tab:trashdata}Republic/Santek Merger Simulation Inputs}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rrccccc}
\toprule
Disposal Firm & Collection Firm & Volume (000s) & Disposal Price (\$) & Disposal Margin (\$) & Collection Margin (\$) & Collection Price (\$)\\
\midrule
Republic & Republic & 165 & 42 & 0 & 44 & 179\\
\cmidrule{1-7}
 & Republic & 34 & 36 & 20 &  & 173\\

>>>>

\caption{\label{tab:trashdata}Republic/Santek Merger Simulation Inputs. Prices and margins are reported in dollars, while volume is reported in thousands of pounds.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rrccccc}
\toprule
Disposal Firm & Collection Firm & Volume & Disposal Price & Disposal Margin & Collection Margin & Collection Price\\
\midrule
Republic & Republic & 165 & 42 & 0 & 44 & 179\\
\cmidrule{1-7}
 & Republic & 34 & 36 & 20 &  & 173\\
